Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-07-08 manuscript/manuscript.Rmd
aligning rmd with Google doc

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
csl               : "apa7.csl"
class             : "man"
output            : 
  papaja::apa6_word

@@

Difficulty establishing the analytic reproducibility of research reports has been encountered in several scientific domains, including economics, political science, behavioural ecology, and psychology [@chang2015; @eubank2016; @stodden2018; @obels2019; @hardwicke2018a; @minocher2020; but see @naudet2018]. A preliminary obstacle for many such studies is that research data are typically unavailable [@hardwicke2018; @hardwicke2020a; @wicherts2006]. Even when data can be accessed, suboptimal management and inadequate documentation can complicate data reuse [@hardwicke2018a; @kidwell2016]. These failures to adequately preserve and share earlier stages of the research pipeline typically prevent downstream assessment of analytic reproducibility.

@@

In the present study, we intended to investigate whether the findings of @hardwicke2018a extended to a corpus of Psychological Science articles that received an ‘open data badge’ to signal data availability. In order to focus specifically on the reproducibility of the analysis process rather than upstream data availability or management practices, we selected only articles that had reusable data according to a previous study [@kidwell2016]. The submission guidelines of Psychological Science specifically stated that authors could earn an open data badge for “making publicly available the digitally-shareable data necessary to reproduce the reported result.” [^psychsci1] Additionally, authors were asked to self-certify that they had provided “…sufficient information for an independent researcher to reproduce the reported results.” [^psychsci2] Thus, if this policy was operating as intended, all numbers presented in these articles should be independently reproducible. If not, we hoped to learn about causes of non-reproducibility in order to identify areas for improvement in journal policy and research practice.

@@

We classified articles as ‘not fully reproducible’ (any major numerical discrepancies, decision errors, or insufficient information to proceed) or ‘reproducible’ (no numerical discrepancies or minor numerical discrepancies only) and noted whether author involvement was provided or not. We recorded the potential causal loci of non-reproducibility and judged the likelihood that non-reproducibility impacted conclusions drawn in the original articles. Team members provided a subjective estimate of the time they spent on each reproducibility check. Additional procedural details are available in Supplementary Information \@ref(sup_design).

@@

The results can be considered at several layers of granularity. Detailed qualitative information about each reproducibility check is available in the individual reproducibility reports (https://osf.io/hf9jy/) and summarized in a short ‘vignette’ available in Supplementary Information \@ref(vignettes). We report descriptive and inferential statistics at the article-level and value-level. We report descriptive and inferential[^infStat] statistics at the article-level and value-level. Ninety-five per cent confidence intervals (CIs) are displayed in square brackets.

@@

<div id = "refs"></div>

```{r child = "supplementary_information.Rmd"}
```

>>>>

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
csl               : "apa7.csl"
class             : "man"
output            : 
  papaja::apa6_pdf:
    includes:
        after_body: "supplementary_information.tex"

@@

Difficulty establishing the analytic reproducibility of research reports has been encountered in several scientific domains, including economics, political science, behavioural ecology, and psychology [@chang2015; @eubank2016; @stodden2018; @obels2019; @hardwicke2018a; @minocher2020; but see @naudet2018]. A preliminary obstacle for many such studies is that research data are typically unavailable [@hardwicke2018; @hardwicke2020a; @wicherts2006]. Even when data can be accessed, suboptimal data management and inadequate documentation can complicate data reuse [@hardwicke2018a; @kidwell2016]. These failures to adequately preserve and share earlier stages of the research pipeline typically prevent downstream assessment of analytic reproducibility.

@@

In the present study, we intended to investigate whether the findings of @hardwicke2018a extended to a corpus of Psychological Science articles that received an ‘open data badge’ to signal data availability. In order to focus specifically on the reproducibility of the analysis process rather than upstream data availability or data management practices, we selected only articles that had reusable data according to a previous study [@kidwell2016]. The submission guidelines of Psychological Science specifically stated that authors could earn an open data badge for “making publicly available the digitally-shareable data necessary to reproduce the reported result.” [^psychsci1] Additionally, authors were asked to self-certify that they had provided “…sufficient information for an independent researcher to reproduce the reported results.” [^psychsci2] Thus, if this policy was operating as intended, all numbers presented in these articles should be independently reproducible. If not, we hoped to learn about causes of non-reproducibility in order to identify areas for improvement in journal policy and research practice.

@@

We classified articles as ‘not fully reproducible’ (any major numerical discrepancies, decision errors, or insufficient information to proceed) or ‘reproducible’ (no numerical discrepancies or minor numerical discrepancies only) and noted whether author involvement was provided or not. We recorded the potential causal loci of non-reproducibility and judged the likelihood that non-reproducibility impacted conclusions drawn in the original articles. Team members provided a subjective estimate of the time they spent on each reproducibility check. Additional design details are available in Supplementary Information \@ref(sup_design).

@@

The results can be considered at several layers of granularity. Detailed qualitative information about each reproducibility check is available in the individual reproducibility reports (https://osf.io/hf9jy/) and summarized in a short ‘vignette’ available in Supplementary Information \@ref(vignettes). We report descriptive and inferential[^infStat] statistics at the article-level and value-level. Ninety-five per cent confidence intervals (CIs) are displayed in square brackets.

@@

```{r render_appendix, include=FALSE}
render_appendix("supplementary_information.Rmd")
```
